This code analyses the representativness of the data in the systematic review

The imput CSV for this code has columns;
- paper - the name of the source paper
- Location_Continent - the continent where the datapoint was collected
- Latitude_class - the latitude of the location of the datapoint, split into tropical, temperate, boreal, and unknown
- peat_type - the type of peatland
- depth_class - the depth of the sample, split into 10 cm categories
- n - number of data points

```{r}
library(tidyverse)
library("viridis")  
```

```{r}
## load data from CSV 
dat <- read_csv("./datasets/all_data.csv")
glimpse(dat)
```

```{r}
# calculating the percentage of each type of peatland
type <- aggregate(n ~ peat_type, data=dat, sum) #SUMIF function
type$percentage <- prop.table(type$n, margin = NULL)*100
type
```


```{r}
# plotting the peat types onto a barplot
q <- type %>%
  mutate(peat_type = fct_reorder(peat_type, n)) %>% #reordering by value of n
  ggplot(aes(x=peat_type, y=n, fill=peat_type)) + 
    geom_bar(stat = "identity") +
    scale_color_viridis(discrete = TRUE, option = "D", direction = -1)+
    scale_fill_viridis(discrete = TRUE, direction = -1) +
    xlab("") +
    ylab("Datapoints (n)") +
    coord_flip()+
    theme_classic()+
    theme(legend.position="none", 
          axis.title = element_text(size=15),  
          axis.text = element_text(size=15))  

ggsave("./output_graphs/peat_type_distribution.png",
  plot = last_plot())
q
```

```{r}
# calculating the percentage of each depth category
depth <- aggregate(n ~ depth_class, data=dat, sum) #SUMIF function
depth$percentage <- prop.table(depth$n, margin = NULL)*100
depth
```

```{r}
# plotting the sample depth categories onto a barplot
p <- depth %>%
  mutate(depth_class = fct_relevel(depth_class,"Unknown","Range >10cm",">50 cm", "41-50 cm","31-40 cm",
              "21-30 cm","11-20 cm","<10 cm")) %>% #reordering by set order
  ggplot(aes(x=depth_class, y=n, fill=depth_class)) + 
    geom_bar(stat = "identity") + #required for this type of plot
    scale_fill_viridis(discrete = TRUE, option = "B") +
    xlab("") + # no x label
    ylab("Datapoints (n)") +
    coord_flip() + #rotate horozontal
    theme_classic()+ #classic theme
    theme(legend.position="none",  #no legend
          axis.title = element_text(size=15),  
          axis.text = element_text(size=15))  
  
ggsave("./output_graphs/depth_distribution.png",
  plot = last_plot())
p
```

```{r}
# calculating the percentage of samples from each continent
continent <- aggregate(n ~ Location_Continent, data=dat, sum) #SUMIF function
continent$percentage <- prop.table(continent$n, margin = NULL)*100
continent
```

```{r}
# calculating the percentage of samples from each latitude class
lat <- aggregate(n ~ Latitude_class, data=dat, sum) #SUMIF function
lat$percentage <- prop.table(lat$n, margin = NULL)*100
lat
```