processing based on: https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/pooling-es.html#pooling-cor

meta package documentation https://cran.r-project.org/web/packages/meta/meta.pdf

```{r}
#install library packagages
library(tidyverse)
library(meta)
```
This code uses the metacor function in meta to do the meta- analysis on data with correlational effects

The CSV for meta-analysis using this code has columns;
- paper - the name of the source paper (label applied in forest plots)
- Hyd_enzyme - a subgroup 
- peat_type - a subgroup
- depth_class - a subgroup
- duration - a subgroup
- subgroup - a subgroup not used for analysis, but to clarify distinctions between subgroups from the same paper
- n - number of data points, a required field for the meta-analysis
- r - the correlation effect, a required field for the meta-analysis

Note: for subgroup analysis, the order the subgroup categories appear vertically in csv columns governs order of subgroups on forest plot

```{r}
## load data from CSV containing correlations (r) and n values
res.all <- read_csv("./datasets/example_metaanalysis-metacor.csv")
glimpse(res.all)
```

```{r}
#meta analysis using a random effects model - all samples
m.cor.all <- metacor(data = res.all,
                 cor = r, 
                 n = n,
                 studlab = paper,
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "REML",
                 method.random.ci = "HK",
                 keepdata = TRUE,
                 )
summary(m.cor.all)
```

```{r}
# create png forest plot for all sample
png(file = "./output_figures/metacor_forest_plot.png", width = 9500, height = 18000, res = 600)


forest(m.cor.all,
       sortvar = TE,
       random = TRUE,
       text.random = "Overall effect",
       label.left = "Negative correlation",
       label.right = "Positive correlation",
       leftcols = c("paper", "Hyd_enzyme", "PO_enzyme", "peat_type","depth_class","subgroup","n"),
       leftlabs = c("Study\n", "Hydrolase \nEnzyme","Oxioreductase \n Enzyme", "Peatland type\n", "Depth \n/cm","Subgroup\n","n\n"),
       rightcols = c("effect","w.random"),
       rightlabs = c("Correlation \n(r)", "Weight\n"),
       test.overall.random = TRUE,
       print.stat = TRUE,
       xlim=c(-1,1)
       )

dev.off()
```

```{r}
#meta analysis using a random effects model - hydrolase enzyme subgroup analysis
m.cor.hyd <- metacor(data = res.all,
                 cor = r, 
                 n = n,
                 studlab = paper,
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "REML",
                 method.random.ci = "HK",
                 keepdata = TRUE,
                 subgroup = Hyd_enzyme,
                 tau.common = FALSE
                 )
```

```{r}
#meta analysis using a random effects model - PO enzyme subgroup analysis
m.cor.PO <- metacor(data = res.all,
                 cor = r, 
                 n = n,
                 studlab = paper,
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "REML",
                 method.random.ci = "HK",
                 keepdata = TRUE,
                 subgroup = PO_enzyme,
                 tau.common = FALSE
                 )
```

```{r}
#meta analysis using a random effects model - peat type subgroup analysis
m.cor.typ <- metacor(data = res.all,
                 cor = r, 
                 n = n,
                 studlab = paper,
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "REML",
                 method.random.ci = "HK",
                 keepdata = TRUE,
                 subgroup = peat_type,
                 tau.common = FALSE
                 )
```

```{r}
#meta analysis using a random effects model - sample depth subgroup analysis
m.cor.dep <- metacor(data = res.all,
                 cor = r, 
                 n = n,
                 studlab = paper,
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "REML",
                 method.random.ci = "HK",
                 keepdata = TRUE,
                 subgroup = depth_class,
                 tau.common = FALSE
                 )
```

```{r}
#meta analysis using a random effects model - intervention duration analysis
m.cor.dur <- metacor(data = res.all,
                 cor = r, 
                 n = n,
                 studlab = paper,
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "REML",
                 method.random.ci = "HK",
                 keepdata = TRUE,
                 subgroup = duration,
                 tau.common = FALSE
                 )

```

```{r}
# combining metaanalyses for different subgroups
m.bind.sub <- metabind(m.cor.hyd, m.cor.PO, m.cor.typ, m.cor.dep,m.cor.dur,
                       name = c ("Hydrolase Enzyme", "Oxioreductase Enzyme", "Peatland type", "Sample depth", "Intervention duration"),
                      random = TRUE)

summary(m.bind.sub)                      
```

```{r}
# create png plot for subgroup analysis
png(file = "./output_figures/metacor_forest_plot_subgroups.png", width = 5250, height = 5400, res = 600)


forest(m.bind.sub,
       random = TRUE, # use random effects model
       text.random = "Overall effect", # label for overall effect
       label.left = "Negative correlation", # labels for the sides of the axis
       label.right = "Positive correlation",
       xlim=c(-1,1), # axis values
       rightlabs = c("r\n", "95% CI\n"), #labels of the right side
       leftlabs = c('Subgroup\n', "Datapoints\n (k)", "Subgroup \nP-value" ),
       overall.hetstat = F,
       test.overall.random = TRUE, #include p-value test for overall summary
       )

dev.off()
```

```{r}
#create funnel plot for risk of missing studies bias assessment
png(file = "./output_funnelplots/metacor_funnel_plot.png",width = 4000, height = 3000, res = 600)

funnel(m.cor.all, random=T, level = 0.95, contour = c(0.9, 0.95, 0.99)) 

dev.off()
```

```{r}
#Egger's test for funnel plot asymmetry
metabias(m.cor.all, method.bias = "Egger")
```

```{r}
#trimfill procedure on the meta-analysis of all results
tf <- trimfill(m.cor.all)
tf
```
