processing based on: https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/pooling-es.html#pooling-cor

meta package documentation https://cran.r-project.org/web/packages/meta/meta.pdf

```{r}
library(tidyverse)
library(meta)
library(robvis)
library(dplyr)
``` 

This code analyses risk of bias assessment for the meta-analyses.

The imput CSV for the analysis by study
- study - the name of the source paper
- D1-6 - 6 columns with the results of the risk of bias assessment in 6 domains categorised as 1-3 (low - high risk of bias), or NA if that category is not relevant to a particular study
- ranking - an overall assessment of the risk of bias for the study as a string (low, high, unclear)
- weight - required for robvis package

```{r}
## load data from CSV containing ROB data
ROB <- read_csv("./datasets/ROB.csv")
glimpse(ROB)
```

```{r}
#creating risk of bias object
r1 <- rob(studlab =ROB$Study, 
    item1=ROB$D1,
    item2=ROB$D2,
    item3=ROB$D3,
    item4=ROB$D4,
    item5=ROB$D5,
    item6=ROB$D6,
    overall=ROB$Ranking,
    categories=c("High risk of bias", "Unclear risk of bias", "Low risk of bias"),
    col=c("red3", "yellow","chartreuse" ),
    symbols=c("-", "?", "+"),
    domains=c("Details about site(s)/peat","Details of methodology","Exposure of samples to oxygen","Representativeness of sampling across site(s)","Similarity of control or comparisons","Extent of intervention/comparison")
    )

r1
```

```{r}
#creating traffic light plot from ROB item
png(file = "./output_graphs/ROB_trafficlight_plot.png",width = 7000, height = 18000, res = 600)

traffic_light(r1,psize=10)+theme(strip.text.y.left = element_text(angle = 0))

dev.off()
```

```{r}
# counting the risk of bias categories in each domain, adding this to a new dataframe
counts <- ROB %>%
  pivot_longer(
    cols = c(D1, D2, D3, D4, D5, D6),
    names_to = "Domain",
    values_to = "Category"
  ) %>%
  filter(Category %in% 1:3) %>%
  count(Domain, Category)

counts <- counts %>%
  mutate(
    Category = case_when(
      Category == 1 ~ "Low",
      Category == 2 ~ "Unclear",
      Category == 3 ~ "High"
    )
  )

# adding in the overall counts from the 'Ranking' column in the original dataframe
ranking_counts <- ROB %>%
  count(Ranking) %>%
  rename(Column = "Ranking", Category = "Ranking")

# add a constant 'Column' value
ranking_counts <- ranking_counts %>%
  mutate(Domain = "Overall")

# bind the ranking counts to the counts_ROB:
counts_ROB <- bind_rows(counts, ranking_counts)

#changing the names of domains
new_labels <- c("Details about site(s)/peat","Details of methodology","Exposure of samples to oxygen","Representativeness of sampling across site(s)","Similarity of control or comparisons","Extent of intervention/comparison")

counts_ROB <- counts_ROB %>%
  mutate(
    Domain = recode(Domain, 
                      "D1" = new_labels[1], 
                      "D2" = new_labels[2], 
                      "D3" = new_labels[3], 
                      "D4" = new_labels[4], 
                      "D5" = new_labels[5], 
                      "D6" = new_labels[6])
  )

counts_ROB
```

```{r}
# create png plot for subgroup analysis
png(file = "./output_graphs/ROB_domains.png", width = 6000, height = 3000, res = 600)

# A stacked barplot
counts_ROB %>%
    mutate(Domain = fct_relevel(Domain,"Details about site(s)/peat","Details of methodology","Exposure of samples to oxygen","Representativeness of sampling across site(s)","Similarity of control or comparisons","Extent of intervention/comparison", "Overall")) %>% #reordering by set order
    mutate (`Category` = fct_relevel(`Category`, "Low", "Unclear", "High")) %>%
    ggplot(aes(x=n, y=Domain, fill=`Category`)) +
    geom_bar(position="fill", stat="identity", width = 0.5) +
        scale_fill_manual(values=c("red3", "yellow", "chartreuse"))+
    xlab("Proportion")+
    scale_y_discrete(limits=rev)+
    theme_bw(base_size = 14)

dev.off()

```

The imput CSV for the analysis by meta-analysis
- Meta-analysis - label for the 6 meta-analyses
- Risk of bias - category
- n - count

```{r}
## load data from CSV containing ROB data
m_ROB <- read_csv("./datasets/ROB_metaanalyses.csv")
glimpse(m_ROB)
```

```{r}
# A stacked barplot
m <- m_ROB %>%
    mutate(`Meta-analysis` = fct_relevel(`Meta-analysis`,"A","B","C","D","E","F")) %>% #reordering by set order
    mutate (`Risk of bias` = fct_relevel(`Risk of bias`, "High", "Unclear", "Low")) %>%
    ggplot(aes(x=n, y=`Meta-analysis`, fill=`Risk of bias`)) +
    geom_bar(position="fill", stat="identity", width = 0.5) +
    #scale_fill_viridis(discrete=TRUE, name="") +
    #theme_ipsum() +
    scale_fill_manual(values=c("chartreuse", "yellow", "red3"))+
    xlab("Proportion")+
    scale_y_discrete(limits=rev)

ggsave("./output_graphs/ROB_metaanalyses.png",
  plot = last_plot())

m
```